\blue{...Numerical investigation of viscous flow instabilities through heterogeneous porous media using adaptive and unstructured meshes under different mobility scenarios...}

### 2017-07-23 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
do not rush kostas
3D case updates

%%%%%%%%%%%% 
\subsection{Initial Model Validation}\label{section:results_validation}
Numerical simulations \citep[based on lab experiments due to][]{evans_1994,dawe_2008} were conducted to demonstrates the model capability to capture viscous crossflow in immiscible displacement in heterogeneous porous media. The 2D domain, shown in Fig.~\ref{fem_cv_represent_a}, is $4$ $\times$ $2$ unit-length and fully saturated with fluid 2 ({\it VR}=1). Fluid 1 is injected from the left-hand side of the domain with constant velocity of $u=1$. Boundary conditions also include no-flux across upper and lower borders. The domain consists of four regions in which each quarter is represented by a permeability value, Fig.~\ref{fem_cv_represent_a}(a). The spatial discontinuities of permeability distribution will create a rough pressure field, \ie the pressure gradient is discontinuous across the interface between different permeability zones thus the flow will be lead to the high permeability region. This fact will cause difficulties for numerically solving fluid flows in heterogeneous porous media.

@@

\blue{(a) Little intro of the case; (b) set up what are the main issues (theory) of the simulations you are showing in this section; (c) then briefly describe what are the strategies to tackle these issues; (d) then describe the numerical experiment w all BC and IC; (e) then finally describe the results with a clear conclusion based on observation but backed by theory and/or physics!!}

>>>>

%%%%%%%%%%%% 
\subsection{Initial Model Validation}\label{section:results_validation}
Numerical simulations \citep[based on lab experiments due to][]{evans_1994,dawe_2008} were conducted to demonstrates the model capability to capture viscous crossflow in immiscible displacement in heterogeneous porous media. The 2D domain, shown in Fig.~\ref{fem_cv_represent_a}, is $4$ $\times$ $2$ unit-length and fully saturated with fluid 2 ({\it VR}=1). Fluid 1 is injected from the left-hand side of the domain with constant velocity of $u=1$. Boundary conditions also include no-flux across upper and lower borders. The domain consists of four regions in which each quarter is represented by a permeability value, Fig.~\ref{fem_cv_represent_a}(a). The spatial discontinuities of permeability distribution will create a rough pressure field, \ie the pressure gradient is discontinuous across the interface between different permeability zones thus the flow will be lead to the high permeability region. This will cause difficulties for numerically solving fluid flows in heterogeneous porous media.

@@

\blue{(a) Little intro of the case;} 
The last of the simulations is related with the effort to describe the finger evolution and the idea of the prefereable path using 3D domain with different permeability regions as these are decribed by figure \ref{fig:3DChannel_PermMesh}.

\blue{(b) set up what are the main issues (theory) of the simulations you are showing in this section;}
\textit{Viscous fingering} is characterized by the formation of a characteristic pattern, called
viscous fingers. The geometrical evolution of these patterns provides good indications about the evolution of the penetration into a zone with a less viscous fluid.

\blue{(c) then briefly describe what are the strategies to tackle these issues; }
Capturing and tracking the  evolution of viscous fingers is important for the understanding the penetration process and fluid patterns that will be created.

\blue{(d) then describe the numerical experiment w all BC and IC; (e) then finally describe the results with a clear conclusion based on observation but backed by theory and/or physics!!}
